---
title: "Airbnb: Data Modeling"
author: "Tanya Bonilla"
date: "11/20/2019"
output: html_document
---

# Predictions


Inititally, I was researching to find out how much people are willing to spend on staying in other people's homes and the effect it has had on hotels, but due to the fact I could not find data that could answer that question I decided to take another route. I'm predicting that the price of a listing is affected by the amount of bedrooms available. 

NOTE TO SELF: use old dataset to further expand on predictions
  - create model with old data set too along with new one
  
# Gettting started

We begin by loading in *Airbnb: Tidying the Data* and any library that we plan on using throughout our analysis.
```{r message=FALSE, error=FALSE, warning=FALSE, results='hide'}
library(rvest)
library(knitr)
library(tidyr)
library(tidyverse)
library(dplyr)
library(caret)
library(jsonlite)
library(ggplot2)

purl("p01_airbnb.Rmd", output = "first_del.r")
source("first_del.r")
```

# Loading and Tidying the Data

We now load in this New York json file we acquired from *Opendatasoft.com* which is a "data sharing platform teams use to access, reuse and share data that grows business." We utilze the function ***fromJSON*** from the jsonlite library. 
```{r}
new_york <- fromJSON("airbnb-listings.json")
colnames(new_york)
```

When looking at the file, we see that there are 5 variables:

* **datasetid** - character type with the id of which the data is from
* **recordid** - character type with the recordid of the listing 
* **geometry**- dataframe with 2 columns with the listing's coordinates
```{r echo = FALSE}
colnames(new_york$geometry)
```
* **fields** - dataframe with 86 variables with details from the listing
```{r echo = FALSE} 
colnames(new_york$fields)
```
+ **record_timestamp** - character 

As we are more interested in the ***fields*** dataframe within the JSON data, let's create a tibble that will hold the variables we deem important for modeling.
```{r}
new_york_fields <- tibble ( 
  price = new_york$fields$price,
  bathrooms = new_york$fields$bathrooms,
  bedrooms = new_york$fields$bedrooms,
  host_neighbourhood = new_york$fields$host_neighbourhood,
  street = new_york$fields$street,
  property_type = new_york$fields$property_type,
  availability_365  = new_york$fields$availability_365,
  zipcode = new_york$fields$zipcode,
  host_location = new_york$fields$host_location,
  host_listings_count = new_york$fields$host_listings_count,
  neighbourhood_group_cleansed = new_york$fields$neighbourhood_group_cleansed,
  host_id = new_york$fields$host_id,
  neighbourhood = new_york$fields$neighbourhood,
  bed_type = new_york$fields$bed_type,
  calendar_last_scraped = new_york$fields$calendar_last_scraped,
  record_timestamp = new_york$record_timestamp
)
new_york_fields <- new_york_fields %>% drop_na()

```

# Modeling

Now that we have our new dataframe, we can focus on modeling the data. The plan is to find if there is any sort of relationship between the listing's price and bedrooms as we are looking to see if there is any relationship between the two. 

```{r}

set.seed(385)
sample_selection <- createDataPartition(new_york_fields$price, p = 0.70, list = FALSE)
train <- new_york_fields[sample_selection,]
test <- new_york_fields[-sample_selection,]
train_model <- lm(price ~ bedrooms, data = train)
predictions <- train_model %>% predict(test)
```

Now that we made the model, we can look at the R^2^ which is a "...statistical measure of how close the data are to the fitted regression line" and mean absolute error (MAE) which is a "measure of difference between two continuous variables." The bigger R^2^ is the better and the smaller MAE the better.
```{r}
summary(train_model)
R2(predictions, test$price)
MAE(predictions, test$price)
```
As we can see, R^2^ is ~0.22-.23 which is much smaller than we would want. Along with MAE, which is much larger than we would want too as it is ~75.6. 

```{r}
ggplot(train, aes(x = train$bedrooms, y = train$price)) + geom_jitter()
```

If we also take into consideration the model's p-value, we see that it is less than 2.2e^-6^ meaning there is clearly no correlation between bedrooms and price. Thus, proving our prediction false.